\bibitem[\protect\citeauthoryear{Aknin, Barrington-Leigh, Dunn, Helliwell,
  Burns, Biswas-Diener, Kemeza, Nyende, Ashton-James, and Norton}{Aknin
  et~al.}{2013}]{aknin13}
\textsc{Aknin, L.~B., C.~P. Barrington-Leigh, E.~W. Dunn, J.~F. Helliwell,
  J.~Burns, R.~Biswas-Diener, I.~Kemeza, P.~Nyende, C.~E. Ashton-James, and
  M.~I. Norton} (2013): \enquote{Prosocial spending and well-being:
  Cross-cultural evidence for a psychological universal.} \emph{Journal of
  Personality and Social Psychology}, 104, 635.

\bibitem[\protect\citeauthoryear{Alesina, Glaeser, and Sacerdote}{Alesina
  et~al.}{2001}]{alesina01}
\textsc{Alesina, A., E.~L. Glaeser, and B.~Sacerdote} (2001): \enquote{Why
  Doesn't the United States Have a European-Style Welfare State,}
  \emph{Brookings Papers on Economic Activity}, 187--254.

\bibitem[\protect\citeauthoryear{Alesina, Glaeser, and Sacerdote}{Alesina
  et~al.}{2005}]{alesina05al}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2005): \enquote{Work and Leisure in the
  U.S. and Europe: Why So Different?} Working Paper 278, National Bureau of
  Economic Research.

\bibitem[\protect\citeauthoryear{Alvarez-Diaz, Gonzalez, and
  Radcliff}{Alvarez-Diaz et~al.}{2009}]{alvarez09}
\textsc{Alvarez-Diaz, A., L.~Gonzalez, and B.~Radcliff} (2009): \enquote{{The
  politics of happiness: On the political determinants of quality of life in
  the American States},} \emph{Unpublished Manuscript}.

\bibitem[\protect\citeauthoryear{Amit and Litwin}{Amit and
  Litwin}{2010}]{amit2010subjective}
\textsc{Amit, K. and H.~Litwin} (2010): \enquote{The subjective well-being of
  immigrants aged 50 and older in Israel,} \emph{Social indicators research},
  98, 89--104.

\bibitem[\protect\citeauthoryear{Anderson, Damianakis, Kr{\"o}ger, Wagner,
  Dawson, Binns, Bernstein, Caspi, and Cook}{Anderson
  et~al.}{2014}]{anderson14}
\textsc{Anderson, N.~D., T.~Damianakis, E.~Kr{\"o}ger, L.~M. Wagner, D.~R.
  Dawson, M.~A. Binns, S.~Bernstein, E.~Caspi, and S.~L. Cook} (2014):
  \enquote{The benefits associated with volunteering among seniors: a critical
  review and recommendations for future research.} \emph{Psychological
  bulletin}, 140, 1505.

\bibitem[\protect\citeauthoryear{Angelini, Cavapozzi, Corazzini, and
  Paccagnella}{Angelini et~al.}{2012}]{angelini2012age}
\textsc{Angelini, V., D.~Cavapozzi, L.~Corazzini, and O.~Paccagnella} (2012):
  \enquote{Age, health and life satisfaction among older Europeans,}
  \emph{Social indicators research}, 105, 293--308.

\bibitem[\protect\citeauthoryear{Ashkanasy}{Ashkanasy}{2011}]{ashkanasy11}
\textsc{Ashkanasy, N.~M.} (2011): \enquote{International Happiness: A
  Multilevel Perspective,} \emph{The Academy of Management Perspectives}, 25,
  23--29.

\bibitem[\protect\citeauthoryear{Bender}{Bender}{2012}]{bender12}
\textsc{Bender, K.~A.} (2012): \enquote{An analysis of well-being in
  retirement: The role of pensions, health, of retirement,} \emph{The Journal
  of Socio-Economics}, 41, 424--433.

\bibitem[\protect\citeauthoryear{Blanchflower and Oswald}{Blanchflower and
  Oswald}{2011}]{blanchflower11}
\textsc{Blanchflower, D.~G. and A.~J. Oswald} (2011): \enquote{International
  happiness: A new view on the measure of performance,} \emph{The Academy of
  Management Perspectives}, 25, 6--22.

\bibitem[\protect\citeauthoryear{Blom and Schr{\"o}der}{Blom and
  Schr{\"o}der}{2011}]{blom2011sample}
\textsc{Blom, A.~G. and M.~Schr{\"o}der} (2011): \enquote{Sample composition 4
  years on: retention in SHARE Wave 3,} \emph{Retrospective data collection in
  the Survey of Health, Ageing and Retirement in Europe}, 55--61.

\bibitem[\protect\citeauthoryear{Bok}{Bok}{2010}]{bok10}
\textsc{Bok, D.} (2010): \emph{The politics of happiness: What government can
  learn from the new research on well-being}, Princeton University Press,
  Princeton NJ.

\bibitem[\protect\citeauthoryear{Bonsang and van Soest}{Bonsang and van
  Soest}{2012}]{bonsang12}
\textsc{Bonsang, E. and A.~van Soest} (2012): \enquote{Satisfaction with social
  contacts of older Europeans,} \emph{Social indicators research}, 105,
  273--292.

\bibitem[\protect\citeauthoryear{Borgonovi}{Borgonovi}{2008}]{borgonovi2008doing}
\textsc{Borgonovi, F.} (2008): \enquote{Doing well by doing good. The
  relationship between formal volunteering and self-reported health and
  happiness,} \emph{Social science \& medicine}, 66, 2321--2334.

\bibitem[\protect\citeauthoryear{Butrica and Schaner}{Butrica and
  Schaner}{2005}]{butrica2005satisfaction}
\textsc{Butrica, B.~A. and S.~G. Schaner} (2005): \enquote{Satisfaction and
  engagement in retirement,} .

\bibitem[\protect\citeauthoryear{Campbell, Converse, and Rodgers}{Campbell
  et~al.}{1976}]{campbell76etal}
\textsc{Campbell, A., P.~E. Converse, and W.~L. Rodgers} (1976): \emph{The
  quality of American life: perceptions, evaluations, and satisfactions},
  Russell Sage Foundation, New York NY.

\bibitem[\protect\citeauthoryear{De~Tocqueville}{De~Tocqueville}{2003}]{tocqueville03}
\textsc{De~Tocqueville, A.} (2003): \emph{Democracy in America}, vol.~10,
  Gateway Editions.

\bibitem[\protect\citeauthoryear{{Di Tella} and MacCulloch}{{Di Tella} and
  MacCulloch}{2006}]{ditella06m}
\textsc{{Di Tella}, R. and R.~MacCulloch} (2006): \enquote{Some Uses of
  Happiness Data in Economics,} \emph{The Journal of Economic Perspectives},
  20, 25--46.

\bibitem[\protect\citeauthoryear{{Di Tella}, MacCulloch, and Oswald}{{Di Tella}
  et~al.}{2001{\natexlab{a}}}]{ditella01mob}
\textsc{{Di Tella}, R., R.~J. MacCulloch, and A.~J. Oswald}
  (2001{\natexlab{a}}): \enquote{The macroeconomics of happiness,} Warwick
  Economic Research Papers No 615.

\bibitem[\protect\citeauthoryear{{Di Tella}, MacCulloch, and Oswald}{{Di Tella}
  et~al.}{2001{\natexlab{b}}}]{ditella01moa}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2001{\natexlab{b}}):
  \enquote{Preferences over inflation and unemployment: Evidence from surveys
  of happiness,} \emph{American Economic Review}, 91, 335--341.

\bibitem[\protect\citeauthoryear{Diener}{Diener}{2009}]{diener09}
\textsc{Diener, E.} (2009): \emph{Well-being for public policy}, Oxford
  University Press, New York NY.

\bibitem[\protect\citeauthoryear{Diener and Seligman}{Diener and
  Seligman}{2004}]{diener04s}
\textsc{Diener, E. and M.~E.~P. Seligman} (2004): \enquote{Beyond Money: Toward
  an Economy of Well-being,} \emph{Psychological Science}, 5, 1--31.

\bibitem[\protect\citeauthoryear{Dingemans and Henkens}{Dingemans and
  Henkens}{2014}]{dingemans2014involuntary}
\textsc{Dingemans, E. and K.~Henkens} (2014): \enquote{Involuntary retirement,
  bridge employment, and satisfaction with life: A longitudinal investigation,}
  \emph{Journal of Organizational Behavior}, 35, 575--591.

\bibitem[\protect\citeauthoryear{Dingemans and Henkens}{Dingemans and
  Henkens}{2015}]{dingemans2015retirement}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2015): \enquote{How do retirement dynamics influence mental well-being in later life? A 10-year panel study,}
  \emph{Scand J Work Environ Health}, 41, 16--23.

\bibitem[\protect\citeauthoryear{Dolan, Peasgood, and White}{Dolan  et~al.}{2008}]{dolan08al}
\textsc{Dolan, P., T.~Peasgood, and M.~White} (2008): \enquote{Do We Really
  Know What Makes Us Happy A Review of the Economic Literature on the Factors
  Associated with Subjective Well-being,} \emph{Journal of Economic
  Psychology}, 29, 94--122.

\bibitem[\protect\citeauthoryear{Dulin, Gavala, Stephens, Kostick, and
  McDonald}{Dulin et~al.}{2012}]{dulin2012volunteering}
\textsc{Dulin, P.~L., J.~Gavala, C.~Stephens, M.~Kostick, and J.~McDonald}
  (2012): \enquote{Volunteering predicts happiness among older M{\=a}ori and
  non-M{\=a}ori in the New Zealand health, work, and retirement longitudinal
  study,} \emph{Aging \& mental health}, 16, 617--624.

\bibitem[\protect\citeauthoryear{Easterlin, McVey, Switek, Sawangfa, and
  Zweig}{Easterlin et~al.}{2010}]{easterlin10B}
\textsc{Easterlin, R.~A., L.~A. McVey, M.~Switek, O.~Sawangfa, and J.~S. Zweig}
  (2010): \enquote{The happiness--income paradox revisited,} \emph{Proceedings
  of the National Academy of Sciences}, 107, 22463--22468.

\bibitem[\protect\citeauthoryear{{Ferrer-i-Carbonell} and
  Frijters}{{Ferrer-i-Carbonell} and Frijters}{2004}]{carbonell04}
\textsc{{Ferrer-i-Carbonell}, A. and P.~Frijters} (2004): \enquote{How
  Important is Methodology for the Estimates of the Determinants of Happiness?}
  \emph{Economic Journal}, 114, 641--659.

\bibitem[\protect\citeauthoryear{Ferring and Boll}{Ferring and
  Boll}{2010}]{ferring10}
\textsc{Ferring, D. and T.~Boll} (2010): \enquote{Subjective wellbeing in older
  adults: Current state and gaps of research,} in \emph{Ageing, health and
  pensions in Europe}, ed. by A.~Z. Lans~Bovenberg, Arthur van~Soest, Springer,
  173--212.

\bibitem[\protect\citeauthoryear{Fischer}{Fischer}{2010}]{fischer10}
\textsc{Fischer, C.~S.} (2010): \emph{Made in America: A social history of
  American culture and character}, University of Chicago Press, Chicago IL.

\bibitem[\protect\citeauthoryear{Frijters, Haisken-Denew, and Shields}{Frijters
  et~al.}{2004}]{frijters04}
\textsc{Frijters, P., J.~P. Haisken-Denew, and M.~a. Shields} (2004):
  \enquote{{Money does matter! evidence from increasing real income and life
  satisfaction in east germany following reunification},} \emph{American
  Economic Review}, 94, 730--740.

\bibitem[\protect\citeauthoryear{Gwozdz and Sousa-Poza}{Gwozdz and
  Sousa-Poza}{2010}]{gwozdz10}
\textsc{Gwozdz, W. and A.~Sousa-Poza} (2010): \enquote{Ageing, health and life
  satisfaction of the oldest old: An analysis for Germany,} \emph{Social
  Indicators Research}, 97, 397--417.

\bibitem[\protect\citeauthoryear{Hank and Erlinghagen}{Hank and
  Erlinghagen}{2009}]{hank09}
\textsc{Hank, K. and M.~Erlinghagen} (2009): \enquote{Dynamics of volunteering
  in older Europeans,} \emph{The Gerontologist}, 50, 170--178.

\bibitem[\protect\citeauthoryear{Haski-Leventhal}{Haski-Leventhal}{2009}]{haski09}
\textsc{Haski-Leventhal, D.} (2009): \enquote{Elderly volunteering and
  well-being: A cross-European comparison based on SHARE data,} \emph{Voluntas:
  International Journal of Voluntary and Nonprofit Organizations}, 20,
  388--404.

\bibitem[\protect\citeauthoryear{Hyde, Higgs, Wiggins, and Blane}{Hyde
  et~al.}{2015}]{hyde15}
\textsc{Hyde, M., P.~Higgs, R.~Wiggins, and D.~Blane} (2015): \enquote{A decade
  of research using the CASP scale: key findings and future directions,} .

\bibitem[\protect\citeauthoryear{Hyde, Wiggins, Higgs, and Blane}{Hyde
  et~al.}{2003{\natexlab{a}}}]{hyde03}
\textsc{Hyde, M., R.~D. Wiggins, P.~Higgs, and D.~B. Blane}
  (2003{\natexlab{a}}): \enquote{A measure of quality of life in early old age:
  the theory, development and properties of a needs satisfaction model
  (CASP-19),} \emph{Aging \& mental health}, 7, 186--194.

\bibitem[\protect\citeauthoryear{Hyde, Wiggins, Higgs, and Blane}{Hyde
  et~al.}{2003{\natexlab{b}}}]{hyde2003measure}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2003{\natexlab{b}}): \enquote{A measure
  of quality of life in early old age: the theory, development and properties
  of a needs satisfaction model (CASP-19),} \emph{Aging \& mental health}, 7,
  186--194.

\bibitem[\protect\citeauthoryear{Jenkinson, Dickens, Jones, Thompson-Coon,
  Taylor, Rogers, Bambra, Lang, and Richards}{Jenkinson
  et~al.}{2013}]{jenkinson2013volunteering}
\textsc{Jenkinson, C.~E., A.~P. Dickens, K.~Jones, J.~Thompson-Coon, R.~S.
  Taylor, M.~Rogers, C.~L. Bambra, I.~Lang, and S.~H. Richards} (2013):
  \enquote{Is volunteering a public health intervention? A systematic review
  and meta-analysis of the health and survival of volunteers,} \emph{BMC public
  health}, 13, 773.

\bibitem[\protect\citeauthoryear{J{\"u}rges and van Soest}{J{\"u}rges and van
  Soest}{2012}]{jurges12}
\textsc{J{\"u}rges, H. and A.~van Soest} (2012): \enquote{Comparing the
  well-being of older europeans: Introduction,} \emph{Social indicators
  research}, 105, 187--190.

\bibitem[\protect\citeauthoryear{Kahneman and Deaton}{Kahneman and
  Deaton}{2010}]{kahneman10}
\textsc{Kahneman, D. and A.~Deaton} (2010): \enquote{High income improves
  evaluation of life but not emotional well-being,} \emph{Proceedings of the
  National Academy of Sciences}, 107, 16489--16493.

\bibitem[\protect\citeauthoryear{Kahneman, Diener, and Schwarz}{Kahneman
  et~al.}{1999}]{kahneman99}
\textsc{Kahneman, D., E.~Diener, and N.~Schwarz} (1999): \emph{Well-being:
  Foundations of hedonic psychology}, Russell Sage Foundation.

\bibitem[\protect\citeauthoryear{Kim, Netuveli, Blane, Peasey, Malyutina,
  Simonova, Kubinova, Pajak, Croezen, Bobak et~al.}{Kim
  et~al.}{2015}]{kim2015psychometric}
\textsc{Kim, G.~R., G.~Netuveli, D.~Blane, A.~Peasey, S.~Malyutina,
  G.~Simonova, R.~Kubinova, A.~Pajak, S.~Croezen, M.~Bobak, et~al.} (2015):
  \enquote{Psychometric properties and confirmatory factor analysis of the
  CASP-19, a measure of quality of life in early old age: the HAPIEE study,}
  \emph{Aging \& mental health}, 19, 595--609.

\bibitem[\protect\citeauthoryear{Klein and Kozlowski}{Klein and
  Kozlowski}{2000}]{klein00}
\textsc{Klein, K.~J. and S.~W. Kozlowski} (2000): \enquote{From micro to meso:
  Critical steps in conceptualizing and conducting multilevel research,}
  \emph{Organizational Research Methods}, 3, 211--236.

\bibitem[\protect\citeauthoryear{Knesbeck, Hyde, Higgs, Kurlan, and
  Siegrist}{Knesbeck et~al.}{2005}]{knesbeck2005quality}
\textsc{Knesbeck, O., M.~Hyde, P.~Higgs, R.~Kurlan, and J.~Siegrist} (2005):
  \enquote{Quality of life and well-being,} .

\bibitem[\protect\citeauthoryear{Kushlev, Dunn, and Lucas}{Kushlev
  et~al.}{2015}]{kushlev15}
\textsc{Kushlev, K., E.~W. Dunn, and R.~E. Lucas} (2015): \enquote{Higher
  Income Is Associated With Less Daily Sadness but not More Daily Happiness,}
  \emph{Social Psychological and Personality Science}, 6, 483--489.

\bibitem[\protect\citeauthoryear{Layard}{Layard}{2005}]{layard05}
\textsc{Layard, R.} (2005): \emph{Happiness. Lessons from a new science.}, The
  Penguin Press, New York NY.

\bibitem[\protect\citeauthoryear{Lipset and Marks}{Lipset and
  Marks}{2000}]{lipset00}
\textsc{Lipset, S.~M. and G.~Marks} (2000): \emph{It didn't happen here: why
  socialism failed in the United States}, WW Norton \& Company, New York NY.

\bibitem[\protect\citeauthoryear{Luttmer}{Luttmer}{2005}]{luttmer05}
\textsc{Luttmer, E. F.~P.} (2005): \enquote{Neighbors as Negatives: Relative
  Earnings and Well-Being,} \emph{Quarterly Journal of Economics}, 120,
  963--02.

\bibitem[\protect\citeauthoryear{Mackintosh}{Mackintosh}{2013}]{mackintosh13}
\textsc{Mackintosh, E.} (2013): \enquote{Report: Income Inequality Rising in
  Most Developed Countries,} \emph{Washington Post}.

\bibitem[\protect\citeauthoryear{Maslow}{Maslow}{[1954] 1987}]{maslow87}
\textsc{Maslow, A.} ([1954] 1987): \emph{{Motivation and personality}},
  Longman, 3 ed.

\bibitem[\protect\citeauthoryear{Mazelis}{Mazelis}{2017}]{mazelis2017surviving}
\textsc{Mazelis, J.~M.} (2017): \emph{Surviving Poverty: Creating Sustainable
  Ties Among the Poor}, NYU Press.

\bibitem[\protect\citeauthoryear{Meier and Stutzer}{Meier and
  Stutzer}{2008{\natexlab{a}}}]{meier2008volunteering}
\textsc{Meier, S. and A.~Stutzer} (2008{\natexlab{a}}): \enquote{Is
  volunteering rewarding in itself?} \emph{Economica}, 75, 39--59.

\bibitem[\protect\citeauthoryear{Meier and Stutzer}{Meier and
  Stutzer}{2008{\natexlab{b}}}]{meier08}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2008{\natexlab{b}}): \enquote{Is volunteering rewarding in itself?} \emph{Economica}, 75, 39--59.

\bibitem[\protect\citeauthoryear{Michalos}{Michalos}{1985}]{michalos85}
\textsc{Michalos, A.} (1985): \enquote{Multiple discrepancies theory (MDT),}
  \emph{Social Indicators Research}, 16, 347--413.

\bibitem[\protect\citeauthoryear{Mujcic and Oswald}{Mujcic and
  Oswald}{2017}]{mujcic17}
\textsc{Mujcic, R. and A.~J. Oswald} (2017): \enquote{Is envy harmful to a
  society's psychological health and wellbeing? A longitudinal study of 18,000
  adults,} \emph{Social Science \& Medicine}.

\bibitem[\protect\citeauthoryear{Myers}{Myers}{2000}]{myers00}
\textsc{Myers, D.~G.} (2000): \enquote{The Funds, Friends, and Faith of Happy
  People,} \emph{American Psychologist}, 55, 56--67.

\bibitem[\protect\citeauthoryear{Nikolova and Graham}{Nikolova and
  Graham}{2014}]{nikolova2014employment}
\textsc{Nikolova, M. and C.~Graham} (2014): \enquote{Employment, late-life
  work, retirement, and well-being in Europe and the United States,} \emph{IZA
  Journal of European Labor Studies}, 3, 1--30.

\bibitem[\protect\citeauthoryear{OECD}{OECD}{2008}]{oecd08}
\textsc{OECD} (2008): \enquote{Income inequality and poverty rising in most
  OECD countries,} \emph{OECD Press Release:
  \url{http://www.oecd.org/general/incomeinequalityandpovertyrisinginmostoecdcountries.htm}}.

\bibitem[\protect\citeauthoryear{Okulicz-Kozaryn}{Okulicz-Kozaryn}{2013}]{aok13liavbility}
\textsc{Okulicz-Kozaryn, A.} (2013): \enquote{City Life: Rankings (Livability)
  Versus Perceptions (Satisfaction),} \emph{Social Indicators Research}, 110,
  433--451.

\bibitem[\protect\citeauthoryear{Okulicz-Kozaryn}{Okulicz-Kozaryn}{2016}]{aok_lsPol16}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2016): \enquote{Happiness Research for
  Public Policy and Administration,} \emph{Transforming Government: People,
  Process and Policy}.

\bibitem[\protect\citeauthoryear{Okulicz-Kozaryn, Holmes~IV, and
  Avery}{Okulicz-Kozaryn et~al.}{2014}]{aokJap14}
\textsc{Okulicz-Kozaryn, A., O.~Holmes~IV, and D.~R. Avery} (2014):
  \enquote{The Subjective Well-Being Political Paradox: Happy Welfare States
  and Unhappy Liberals.} \emph{Journal of Applied Psychology}, 99, 1300--1308.

\bibitem[\protect\citeauthoryear{Okulicz-Kozaryn and Mazelis}{Okulicz-Kozaryn
  and Mazelis}{2016}]{aok_ruut_inc_ine}
\textsc{Okulicz-Kozaryn, A. and J.~M. Mazelis} (2016): \enquote{More Unequal In
  Income, More Unequal in Wellbeing,} \emph{Social Indicators Research}.

\bibitem[\protect\citeauthoryear{Okulicz-Kozaryn and Valente}{Okulicz-Kozaryn
  and Valente}{2018}]{aok-swbLivability18}
\textsc{Okulicz-Kozaryn, A. and R.~Valente} (2018): \enquote{Livability and
  Subjective Wellbeing Across European Cities,} \emph{Forthcoming in Applied
  Research in Quality of Life}.

\bibitem[\protect\citeauthoryear{Oswald}{Oswald}{2014}]{oswald14}
\textsc{Oswald, A.} (2014): \enquote{Keynote II,} \emph{2014 Wellbeing and
  Public Policy Conference at Hamilton College}.

\bibitem[\protect\citeauthoryear{Pacek and Radcliff}{Pacek and
  Radcliff}{2008{\natexlab{a}}}]{pacek08b}
\textsc{Pacek, A. and B.~Radcliff} (2008{\natexlab{a}}): \enquote{Assessing the
  welfare state: The politics of happiness,} \emph{Perspectives on Politics},
  6, 267--277.

\bibitem[\protect\citeauthoryear{Pacek and Radcliff}{Pacek and
  Radcliff}{2008{\natexlab{b}}}]{pacek08r}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2008{\natexlab{b}}): \enquote{Welfare
  Policy and Subjective Well-Being Across Nations: An Individual-Level
  Assessment.} \emph{Social Indicators Research}, 89, 179 -- 191.

\bibitem[\protect\citeauthoryear{P{\'e}rez-Rojo, Mart{\'\i}n, Noriega, and
  L{\'o}pez}{P{\'e}rez-Rojo et~al.}{2017}]{perez2017psychometric}
\textsc{P{\'e}rez-Rojo, G., N.~Mart{\'\i}n, C.~Noriega, and J.~L{\'o}pez}
  (2017): \enquote{Psychometric properties of the CASP-12 in a Spanish older
  community dwelling sample,} \emph{Aging \& mental health}, 1--9.

\bibitem[\protect\citeauthoryear{Piketty and Saez}{Piketty and
  Saez}{2003}]{piketty03}
\textsc{Piketty, T. and E.~Saez} (2003): \enquote{Income inequality in the
  United States, 1913--1998,} \emph{The Quarterly Journal of Economics}, 118,
  1--41.

\bibitem[\protect\citeauthoryear{Pruchno, Wilson-Genderson, and
  Cartwright}{Pruchno et~al.}{2010{\natexlab{a}}}]{pruchno2010two}
\textsc{Pruchno, R.~A., M.~Wilson-Genderson, and F.~Cartwright}
  (2010{\natexlab{a}}): \enquote{A two-factor model of successful aging,}
  \emph{Journals of Gerontology Series B: Psychological Sciences and Social
  Sciences}, 65, 671--679.

\bibitem[\protect\citeauthoryear{Pruchno, Wilson-Genderson, Rose, and
  Cartwright}{Pruchno et~al.}{2010{\natexlab{b}}}]{pruchno2010successful}
\textsc{Pruchno, R.~A., M.~Wilson-Genderson, M.~Rose, and F.~Cartwright}
  (2010{\natexlab{b}}): \enquote{Successful aging: Early influences and
  contemporary characteristics,} \emph{The Gerontologist}, 50, 821--833.

\bibitem[\protect\citeauthoryear{Radcliff}{Radcliff}{2001}]{radcliff01}
\textsc{Radcliff, B.} (2001): \enquote{Politics, Markets, and Life
  Satisfaction: The Political Economy of Human Happiness,} \emph{American
  Political Science Review}, 95, 939--952.

\bibitem[\protect\citeauthoryear{Radcliff}{Radcliff}{2013}]{radcliff13}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2013): \emph{The Political Economy of
  Human Happiness: How Voters' Choices Determine the Quality of Life},
  Cambridge University Press, New York NY.

\bibitem[\protect\citeauthoryear{Saegert, Thompson, and Warren}{Saegert
  et~al.}{2002}]{saegert2002social}
\textsc{Saegert, S., J.~P. Thompson, and M.~R. Warren} (2002): \emph{Social
  capital and poor communities}, Russell Sage Foundation.

\bibitem[\protect\citeauthoryear{Scruggs and Allan}{Scruggs and
  Allan}{2006}]{scruggs06Ba}
\textsc{Scruggs, L. and J.~Allan} (2006): \enquote{Welfare-state
  decommodification in 18 OECD countries: A replication and revision,}
  \emph{Journal of European Social Policy}, 16, 55--72.

\bibitem[\protect\citeauthoryear{Stolnitz}{Stolnitz}{1992}]{stolnitz1992demographic}
\textsc{Stolnitz, G.~J.} (1992): \enquote{Demographic causes and economic
  consequences of population aging: Europe and North America.} .

\bibitem[\protect\citeauthoryear{Thaler and Sunstein}{Thaler and
  Sunstein}{2008}]{thaler08}
\textsc{Thaler, R. and C.~Sunstein} (2008): \emph{Nudge: Improving decisions
  about health, wealth, and happiness}, Yale University Press.

\bibitem[\protect\citeauthoryear{Van~Willigen}{Van~Willigen}{2000}]{van2000differential}
\textsc{Van~Willigen, M.} (2000): \enquote{Differential benefits of
  volunteering across the life course,} \emph{The Journals of Gerontology
  Series B: Psychological Sciences and Social Sciences}, 55, S308--S318.

\bibitem[\protect\citeauthoryear{Vanhoutte}{Vanhoutte}{2012}]{vanhoutte12}
\textsc{Vanhoutte, B.} (2012): \enquote{Measuring subjective well-being: a
  review,} \emph{CCSR Woking Paper}.

\bibitem[\protect\citeauthoryear{Vanhoutte}{Vanhoutte}{2014}]{vanhoutte14}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2014): \enquote{The multidimensional
  structure of subjective well-being in later life,} \emph{Journal of
  population ageing}, 7, 1--20.

\bibitem[\protect\citeauthoryear{Vaupel and Loichinger}{Vaupel and
  Loichinger}{2006}]{vaupel2006redistributing}
\textsc{Vaupel, J.~W. and E.~Loichinger} (2006): \enquote{Redistributing work
  in aging Europe,} \emph{Science}, 312, 1911--1913.

\bibitem[\protect\citeauthoryear{Veenhoven}{Veenhoven}{2008}]{veenhoven08}
\textsc{Veenhoven, R.} (2008): \enquote{Sociological theories of subjective
  well-being,} in \emph{The Science of Subjective Well-being: A tribute to Ed
  Diener}, ed. by M.~Eid and R.~Larsen, The Guilford Press, New York NY,
  44--61.

\bibitem[\protect\citeauthoryear{Veenhoven}{Veenhoven}{2012}]{veenhoven12}
---\hspace{-.1pt}---\hspace{-.1pt}--- (2012): \enquote{Evidence-based pursuit
  of happiness: What we should know, what we do know and what we can get to
  know,} Tech. rep., EHERO.

\bibitem[\protect\citeauthoryear{Verbeek}{Verbeek}{2015}]{verbeek15}
\textsc{Verbeek, J.} (2015): \enquote{Increasingly, inequality within, not
  across, countries is rising,} \emph{The World bank Development Talk
  \url{http://blogs.worldbank.org/developmenttalk/increasingly-inequality-within-not-across-countries-rising}}.

\bibitem[\protect\citeauthoryear{Wahrendorf, von~dem Knesebeck, and
  Siegrist}{Wahrendorf et~al.}{2006}]{wahrendorf06}
\textsc{Wahrendorf, M., O.~von~dem Knesebeck, and J.~Siegrist} (2006):
  \enquote{Social productivity and well-being of older people: baseline results
  from the SHARE study,} \emph{European Journal of Ageing}, 3, 67--73.

\bibitem[\protect\citeauthoryear{Wheeler, Gorey, and Greenblatt}{Wheeler
  et~al.}{1998}]{wheeler98}
\textsc{Wheeler, J.~A., K.~M. Gorey, and B.~Greenblatt} (1998): \enquote{The
  beneficial effects of volunteering for older volunteers and the people they
  serve: A meta-analysis,} \emph{The International Journal of Aging and Human
  Development}, 47, 69--79.

\bibitem[\protect\citeauthoryear{Wilson}{Wilson}{2012{\natexlab{a}}}]{wilson12}
\textsc{Wilson, E.~O.} (2012{\natexlab{a}}): \emph{On human nature}, Harvard
  University Press.

\bibitem[\protect\citeauthoryear{Wilson}{Wilson}{2012{\natexlab{b}}}]{wilson12B}
\textsc{Wilson, J.} (2012{\natexlab{b}}): \enquote{Volunteerism research: A
  review essay,} \emph{Nonprofit and Voluntary Sector Quarterly}, 41, 176--212.